---
title: "Linear_Regression_with_LRpkg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear_Regression_with_LRpkg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This is a simple tutorial to demonstrate how to use the 'linreg()' function. We will perform linear regression analysis with the 'iris' dataset and show how to use the other methods in the' LRpkg 'package.

# Load packages and data

First, we load the 'LRpkg' package and use the 'iris' dataset that comes with R:

```{r setup}
library(LRpkg)
library(ggplot2)
data(iris)
```

# Executive linear regression

We use 'Sepal.Length' as the dependent variable and 'Sepal.Width' and 'Petal.Length' as the independent variables for regression:

```{r linreg}
model <- linreg(Sepal.Length ~ Sepal.Width + Petal.Length, data = iris)
```

# Print model result

The regression coefficient can be printed using the 'print()' method:

```{r print}
print(model)
```

# Plot residuals

Check the fit of the model by plotting the residuals using the 'plot()' method:

```{r plot}
plot(model)
```

# Acquired residuals

The resid() method can be used to obtain the residual of the model:

```{r resid}
residuals <- resid(model)
print(residuals)
```

# Output predicted value

We can use the 'pred()' method to get the predicted value of the model:

```{r pred}
predicted_values <- pred(model)
print(predicted_values)
```

# Get the regression coefficient

We can use the coef() method to obtain the regression coefficient:

```{r coef}
coefficients <- coef(model)
print(coefficients)
```

# Model summary

We can also use the 'summary()' method to view detailed statistics of the model, including the standard error, t-value, and p-value of the coefficients:

```{r summary}
summary(model)
```